---
title: "PSY 8960 Week 8 Project"
author: "Joy Zhou"
output:
  html_document:
    df_print: paged
---

### **Reproducible Image and Online Resources**
##### An image of this project as of *`r format(Sys.time(), '%d %B %Y')`* can be accessed by [clicking this link](https://mybinder.org/v2/gh/joyzhou95/psy8960-week8.git/HEAD?urlpath=rstudio).
##### An interactive web app is available by [clicking this link instead]( https://joyzhou.shinyapps.io/shiny_week8/).

### **Script Settings and Resources**
```{r, message = FALSE, warning = FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(DT)
```

### **Data Import and Cleaning**
###### Imported the csv dataset and created all variables that will be used in all subsequent codings to minimize data manipulation in later steps 
###### Used rowwise to aggregate across rows and then calcualted the mean variable using the row means of the selected variables
```{r message = FALSE}
week8_tbl <- read_csv(file = "../data/week3.csv") %>%
  mutate(q5 = recode(q5, "1" = 5, "2" = 4, "4" = 2, "5" = 1)) %>%
  rowwise() %>%
  mutate(q1_q6_mean = mean(c(q1,q2,q3,q4,q5)),
         q8_q10_mean = mean(c(q8,q9,q10)),
         gender = factor(gender, ordered = FALSE, levels = c("M", "F"),labels = c("Male", "Female")))
```

### **Visualization**
###### Displayed paginated data using the DT::datatable function
###### Created the scatterplot between two mean vairiables using ggplot function, jittered it to avoid overplotting and added required settings 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
datatable(week8_tbl) 

week8_tbl %>%
  ggplot(aes(q1_q6_mean, q8_q10_mean)) +
  geom_point(position = "jitter") +
  geom_smooth(method = "lm", color = "purple") 
```

### **Analysis**
###### Displayed correlation and p-value using cor.test and got the specific values from the cor.test output
###### Added texts with the values embedded
```{r}
cor.test(week8_tbl$q1_q6_mean, week8_tbl$q8_q10_mean)
round(cor.test(week8_tbl$q1_q6_mean, week8_tbl$q8_q10_mean)$estimate, 2)
round(cor.test(week8_tbl$q1_q6_mean, week8_tbl$q8_q10_mean)$p.value, 2)
```
I observed a correlation of `r round(cor.test(week8_tbl$q1_q6_mean, week8_tbl$q8_q10_mean)$estimate, 2)` between the mean scores of questions 1-6 and the mean scores of questions 8-10. Given the p-value is  `r round(cor.test(week8_tbl$q1_q6_mean, week8_tbl$q8_q10_mean)$p.value, 2)`, which is larger than 0.05, the correlation is not significant.

### **Data Export**
###### Used saveRDS fucntion to save the dataset in RDS form and in the shiny folder so it can be easily accessed by shiny
###### Saved in the shiny diretory where app.R will be 
```{r}
week8_tbl %>%
  saveRDS(file = "../shiny/week8.rds")
```



